\documentclass{scrartcl}

\usepackage{csquotes}
\usepackage{listings}

\title{Excerpt of: Dafny: An Automatic Program Verifier for Functional Correctness}

\begin{document}
\begin{center}
    \Large{\textbf{Report on}}

    \LARGE{The difference between multiple ways to acquire a log of dafny's/boogie's input
    for Z3}
\end{center}

\vspace{1cm}

The Dafny verifier creates a Boogie program.
Boogie controls Z3 via the SMT-LIB commands.

There are different ways to save what commands Boogie/Dafny actually passes to Z3
given the program \lstinline|program.bpl|/\lstinline|program.dfy|
(\lstinline|program.bpl| can be produced using
\lstinline|dafny /print:program.bpl program.dfy /noVerify|)
in a file called \lstinline|logfile|:
\begin{enumerate}
    \item \lstinline|dafny /proverOpt:PROVER_PATH=logging_z3.sh program.dfy|
        \label{dafny_intercepted}
    \item \lstinline|dafny /proverOpt:LOG_FILE=logfile program.dfy|
        \label{dafny_proveroption}
    \item \lstinline|boogie /proverOpt:PROVER_PATH=logging_z3.sh program.bpl|
        \label{boogie_intercepted}
    \item \lstinline|boogie /proverOpt:LOG_FILE=logfile program.bpl|
        \label{boogie_proveroption}
    \item \lstinline|boogie /proverLog:logfile program.bpl|
        \label{boogie_boogieoption}
\end{enumerate}

Where \lstinline|logging_z3.sh| contains

\begin{lstlisting}[frame=single]
#!/bin/sh
logfilename="$(dirname '$0')/logfile"
tee $logfilename | z3 -in $@
\end{lstlisting}

Superficial examination shows that not every logfile has an equal number of lines.

\begin{tabular}{|l|l|l|}
    \hline
    & Logfile creation & \#lines in logfile \\
    \hline
    \ref{dafny_intercepted} \
    & \lstinline|dafny /proverOpt:PROVER_PATH=logging_z3.sh program.dfy| \
    & \testdafnyproverlogintercepted \\
    \ref{dafny_proveroption} \
    & \lstinline|dafny /proverOpt:LOG_FILE=logfile program.dfy|          \
    & \testdafnyproverlogproveroption \\
    \ref{boogie_intercepted} \
    & \lstinline|boogie /proverOpt:PROVER_PATH=logging_z3.sh program.bpl| \
    & \testboogieproverlogintercepted \\
    \ref{boogie_proveroption} \
    & \lstinline|boogie /proverOpt:LOG_FILE=logfile program.bpl|          \
    & \testboogieproverlogproveroption \\
    \ref{boogie_boogieoption} \
    & \lstinline|boogie /proverLog:logfile program.bpl|                   \
    & \testboogieproverlogboogieoption \\
    - & Total & \total \\
    \hline
\end{tabular}

\section{Comparison by the way of example}
In this section the logfiles, created in the ways described above, are compared.
They all stem from Boogie/Dafny runs on the same Dafny program:
\lstinputlisting[frame=single]{test.dfy}

The logfiles created by \ref{boogie_proveroption} and \ref{boogie_boogieoption} are identical.

The intercepted version (\ref{boogie_intercepted}) contains eight additional lines.
A total of six are \lstinline|(get-info :name)|
at the start in the middle and at the end of the document.
Three lines are prepended:
\begin{lstlisting}[frame=single]
(reset)
(get-info :name)
(set-option :rlimit 0)
\end{lstlisting}

The differneces between \ref{dafny_proveroption} and \ref{dafny_intercepted} are very similar.
The intercepted version (\ref{dafny_intercepted}) contains six additional lines.
A total of four are \lstinline|(get-info :name)|
in the middle and at the end of the document but not at the start.
Two lines are prepended:
\begin{lstlisting}[frame=single]
(reset)
(set-option :rlimit 0)
\end{lstlisting}

There there are 6140 insertions and 6118 deletions between
\ref{boogie_proveroption} and \ref{dafny_proveroption}.

\end{document}
